mir\_eval

### 2014-05-06 paper/paper.tex
Adding introduction first draft

% MIR intends to act like humans
% Human evaluation is costly
% Metrics are used as a proxy

% Evaluation should be easy and standardized
% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, etc.
% As a result many different implementations of metrics, and implementation matters
% mir_eval as the antidote to the above

\section{mir\_eval's architecture}

@@

\section{Tasks included in mir\_eval}

@@

\section{Comparison to Existing Implementations}

@@

\section{Discussion}

>>>>

Many tasks in the field of Music Information Retrieval (MIR) involve the development of systems which can automatically produce semantic information about a piece of music.
The effectiveness of such a system is typically judged based on how similar it acts to a human \cite{downie2003toward}.
A straightforward way to make this judgement would be for a human to study the output produced by the system and judge its correctness.
However, this process is inherently subjective and also extremely time-consuming when evaluating a system's output over a large corpus of music.

As a result, metrics have been defined for each task which provide a well-defined way of computing a score which denotes the correctness of a system's output.
These metrics typically involve a heuristically-motivated comparison of the system's output to a reference which is known to be correct.
Over time, certain metrics have become standard for each task, so that the performance of systems created by different researchers can be compared when they are evaluated over the same dataset \cite{downie2003toward}.
Unfortunately, this comparison can be confounded by the fact that the actual implementation of the metric can affect the scores it produces.

% MIREX is the standard, but it's not community-developed, not transparent, not well-documented, uses multiple languages, is coupled to NEMA, not easy to use, dependencies, not used outside of MIREX, etc.
For the past 10 years, the yearly Music Information Retrieval EXchange (MIREX) has provided setting in which different MIR algorithms may be compared against common datasets \cite{downie2008music}.
By providing a standardized shared-task setting to track progress, MIREX has proven to be critically useful in the evolution of MIR research.
MIREX relies on the Networked Environment for Music Analysis (NEMA) \cite{west2010networked}, a large-scale system which includes exhaustive functionality for evaluating, summarizing, and displaying evaluation results.
The NEMA codebase includes multiple programming languages and dependencies (including proprietary ones, e.g. MATLAB) so compiling and running it for research uses is nontrivial.

Due to its scale, characteristics, and intended use, the NEMA system is rarely used for evaluating MIR algorithms outside of the setting of MIREX \cite{downie2008music}.
As a result, researchers typically create their own implementations of common metrics for evaluating their algorithms.
These implementations are not standardized, and even worse, may contain bugs.
Both of these factors can confound comparison of different systems.

These factors motivate the development of a standardized software package which implements the most common metrics used to evaluate MIR systems.
Such a package should be straightforward to use and well-documented so that it can be easily adopted and understood by MIR researchers.
In addition, it should be community-developed and transparently implemented so that all design decisions are well-reasoned and easily understood.

Motivated by these criteria, we present \mireval, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
The present work first discusses the architecture and design of \mireval in Section \ref{sec:architecture}.
In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval and the metrics included.
In order to validate our implementation decisions, we compare \mireval to existing software in Section \ref{sec:comparison}.
Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.

\section{mir\_eval's architecture}
\label{sec:architecture}

@@

\section{Tasks included in mir\_eval}
\label{sec:tasks}

@@

\section{Comparison to Existing Implementations}
\label{sec:comparison}

@@

\section{Discussion}
\label{sec:discussion}
